---
title: "DataCleaning"
author: "Signe Kløve Kjær"
date: "2/5/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r loading packages, include = FALSE}

#install.packages("tidybayes"); install.packages("LaplacesDemon")
library(brms); library(tidyverse); library(tidybayes); library(ggplot2); library(LaplacesDemon); library(rethinking); library(tidyr); library(reshape2);library(pacman); library(tibble);library(tidyr) ;library(pacman)

p_load(plotly, jpeg)
```



```{r loading data and merging, include = FALSE}
#setwd("~/Cognitive Science/4. Semester/Social and Cultural Dynamics Exam/SocKultExam-master/")
#setwd("~/SocKultExam")
#data_path = ("~/SocKultExam/Data/")


setwd("/Users/signeklovekjaer/Documents/CognitiveScience/4.semester/Social_and_cultural_dynamics_in_cognition/Exam/SocKultExam/")

data_path = ("/Users/signeklovekjaer/Documents/CognitiveScience/4.semester/Social_and_cultural_dynamics_in_cognition/Exam/SocKultExam/Data/")

plot_path = ("/Users/signeklovekjaer/Documents/CognitiveScience/4.semester/Social_and_cultural_dynamics_in_cognition/Exam/SocKultExam/plots/")

#lets loop
files <- list.files(path = data_path)
files

data <- data.frame(matrix(ncol = 36, nrow = 0))


for (i in files) {
  d <- read.delim(file = paste(data_path, i, sep = ""), sep = ",", header = TRUE)
  data = rbind(data,d)
}

#KIRIS DATA
kiri_path = ("~/SocKultExam/")
kiri_files <- list.files(path = kiri_path, pattern = "*.csv")
kiri_files

kiri_data <- data.frame(matrix(ncol = 35, nrow = 0))

for (i in kiri_files) {
  d <- read.delim(file = paste(kiri_path, i, sep = ""), sep = ",", header = TRUE, stringsAsFactors = FALSE)
  kiri_data = rbind(kiri_data, d)
}


#merge the two

kiri_data <- add_column(kiri_data, Computer = "Two screens", .after = 4)

data <- rbind(data, kiri_data)

unique(data$GroupNumber)



```


```{r clean data, include = FALSE}

#CLEAN DATA

data <- subset(data, select = -c(X))

data$GroupNumber[data$GroupNumber == "17_10_30"] <- 17
data$GroupNumber[data$GroupNumber == "18_10_30"] <- 18
data$GroupNumber[data$GroupNumber == "19_10_50"] <- 19
data$GroupNumber[data$GroupNumber == "20_10_50"] <- 20
data$GroupNumber[data$GroupNumber == "21_12_15"] <- 21
data$GroupNumber[data$GroupNumber == "22_12_15"] <- 22
data$GroupNumber[data$GroupNumber == "23_12_40"] <- 23
data$GroupNumber[data$GroupNumber == "24_12_40"] <- 24
data$GroupNumber[data$GroupNumber == "25_15_00"] <- 25
data$GroupNumber[data$GroupNumber == "26_15_00"] <- 26
data$GroupNumber[data$GroupNumber == "27_15_20"] <- 27
data$GroupNumber[data$GroupNumber == "28_15_20"] <- 28
data$GroupNumber[data$GroupNumber == "29_16_00"] <- 29
data$GroupNumber[data$GroupNumber == "30_16_00"] <- 30
data$GroupNumber[data$GroupNumber == "31_16_20"] <- 31
data$GroupNumber[data$GroupNumber == "32_16_20"] <- 32
data$GroupNumber[data$GroupNumber == "33_9_30"] <- 33
data$GroupNumber[data$GroupNumber == "34_09_30"] <- 34
data$GroupNumber[data$GroupNumber == "35_09_50"] <- 35
data$GroupNumber[data$GroupNumber == "36_9_50"] <- 36
data$GroupNumber[data$GroupNumber == "37_26_4"] <- 37
data$GroupNumber[data$GroupNumber == "38_26_4"] <- 38
data$GroupNumber[data$GroupNumber == "39_26_4"] <- 39
data$GroupNumber[data$GroupNumber == "40_26_4"] <- 40

data$SubjectID_left <- as.character(data$SubjectID_left)
data$SubjectID_right <- as.character(data$SubjectID_right)
data$SubjectID_left[data$SubjectID_left == "steph"] <- "stephanie"
data$SubjectID_right[data$SubjectID_right == "Emil"] <- "emil"
data$SubjectID_right[data$SubjectID_right == "Sebber"] <- "seb"
data$SubjectID_left[data$SubjectID_left == "signe"] <- "SigneR"
data$SubjectID_right[data$SubjectID_right == "karo"] <- "Karoline"
data$SubjectID_right[data$SubjectID_right == "tobias"] <- "Toby"
data$SubjectID_left[data$SubjectID_left == "Nina"] <- "nina"
data$SubjectID_right[data$SubjectID_right == "theasmom"] <- "Theasmom"
data$SubjectID_left[data$SubjectID_left == "emma"] <- "Emma"
data$SubjectID_right[data$SubjectID_right == "LasseKob"] <- "Lasse"

```



```{r making variables for sensitivty, include = FALSE}
#Making column, which expresses difficulty
data$dif_blue <- data$Prop_blue_image_1-data$Prop_blue_image_2

#Making a column, which expresses answer of participants, 0 = left picture, 1 = right picture
data$right_answer <- ifelse(data$Response_right > 0, 1, 0)
data$left_answer <- ifelse(data$Response_left > 0, 1, 0)

#Joining joint answer to one column
data$joint_answer <- data$Joint_right+ data$Joint_left

```

```{r coding for leader/follower}

#create a column that sorts out all the agreed trials
data$chosen_leader <- ifelse(data$right_answer == data$left_answer, "Agree", 0) 

data$chosen_leader[data$chosen_leader == 0 & data$Joint_right == 0] <- "Left_lead"

data$chosen_leader[data$chosen_leader == 0 & data$Joint_left == 0] <- "Right_lead"


#create column that specifies the gender of the leader

data$Leader_gender <- 0
data$Leader_gender <- ifelse(data$chosen_leader == "Left_lead", as.character(data$Gender_left), as.character(data$Gender_right))
data$Leader_gender[data$chosen_leader == "Agree"] <- NA

#create column that specifies the gender of the follower

data$Follower_gender <- 0
data$Follower_gender <- ifelse(data$chosen_leader == "Left_lead", as.character(data$Gender_right), as.character(data$Gender_left))
data$Follower_gender[data$chosen_leader == "Agree"] <- NA

```


```{r #did the leader stick?}
data$right_answer[data$right_answer == 0] <- -1
data$left_answer[data$left_answer == 0] <- -1


#leader stubbornness
data$Stubborn_leader <- 0

data$Stubborn_leader[data$chosen_leader == "Right_lead" & data$joint_answer == data$right_answer] <- "stick"
data$Stubborn_leader[data$chosen_leader == "Right_lead" & data$joint_answer != data$right_answer] <- "surrender"

data$Stubborn_leader[data$chosen_leader == "Left_lead" & data$joint_answer == data$left_answer] <- "stick"
data$Stubborn_leader[data$chosen_leader == "Left_lead" & data$joint_answer != data$left_answer] <- "surrender"

data$Stubborn_leader[data$chosen_leader == "Agree"] <- NA


#plot

disagree_data <- na.omit(data)

disagree_data$try <- paste("Leader:", disagree_data$Leader_gender, "_Follower:", disagree_data$Follower_gender, sep = "")
disagree_data$stick <- ifelse(disagree_data$Stubborn_leader == "stick", 1, 0)

ggplot(data = disagree_data, aes(Stubborn_leader, fill = Stubborn_leader)) +
  facet_grid(~try) +
  geom_histogram(stat = "count")


```

Bayesian tutorial on logistic regression: https://www.jamesrrae.com/post/bayesian-logistic-regression-using-brms-part-1/

```{r make unique subject and create three dataframes}
#Making unique subjects
data$unique_ID_right <- paste(data$GroupNumber, data$SubjectID_right, sep = "_")
data$unique_ID_left <- paste(data$GroupNumber, data$SubjectID_left, sep = "_")


#preparing datasets with only correct trails for individuals and joint
left_data <- filter(data, Correct_left == 1)
right_data <- filter(data, Correct_right == 1)
joint_data <- filter(data, Correct_joint == 1)
```


```{r plot difficulty for individuals and joint}
ggplot(data = left_data, aes(Correct_left, fill = dif_blue)) +
  facet_grid(~dif_blue) +
  geom_histogram(stats = "count", binwidth = 0.06) +
  geom_density()

ggplot(data = right_data, aes(Correct_right, fill = dif_blue)) +
  facet_grid(~dif_blue) +
  geom_histogram(stats = "count", binwidth = 0.06)

ggplot(data = joint_data, aes(Correct_joint, fill = dif_blue)) +
  facet_grid(~dif_blue) +
  geom_histogram(stats = "count", binwidth = 0.06)

```

```{r test for one individual skal slettes på et tidspunkt }

data_i <- filter(data, unique_ID_left == "12_Telma")

#THEA
trans_left_path = file.path("~/SocKultExam/plots/transition/left/", paste("trans_left_plot_", ".jpeg", sep = ""))
trans_right_path = file.path("~/SocKultExam/plots/transition/right/", paste("trans_right_plot_", ".jpeg", sep = ""))
trans_joint_path = file.path("~/SocKultExam/plots/transition/joint/", paste("trans_joint_plot_", ".jpeg", sep = ""))

pp_left_path = file.path("~/SocKultExam/plots/pp_check/left/", paste("pp_left_plot_", ".jpeg", sep = ""))
pp_right_path = file.path("~/SocKultExam/plots/pp_check/right/", paste("pp_right_plot_", ".jpeg", sep = ""))
pp_joint_path = file.path("~/SocKultExam/plots/pp_check/joint/", paste("pp_joint_plot_", ".jpeg", sep = ""))


#SIGNE
trans_left_path = file.path("/Users/signeklovekjaer/Documents/CognitiveScience/4.semester/Social_and_cultural_dynamics_in_cognition/Exam/SocKultExam/plots/transition/left/", paste("trans_left_plot_", ".jpeg", sep = ""))


pp_left_path = file.path("/Users/signeklovekjaer/Documents/CognitiveScience/4.semester/Social_and_cultural_dynamics_in_cognition/Exam/SocKultExam/plots/pp_check/left/", paste("pp_left_plot_", ".jpeg", sep = ""))


marginal_left_path = file.path("/Users/signeklovekjaer/Documents/CognitiveScience/4.semester/Social_and_cultural_dynamics_in_cognition/Exam/SocKultExam/plots/marginal/left/", paste("marginal_left_plot_", ".jpeg", sep = ""))




#Defining priors
prior =  c(
prior(normal(0,2), class = "Intercept"), #How to motivate this?
#prior(normal(0,2), class = "sigma"), #Roughly on the same scale
prior(normal(0,2), class = "b"), #How to motiavte this?
prior(normal(0,1), class = "b", coef = "dif_blue"))
  
  #Prior predictive check
prior_check <- brm( left_answer ~ dif_blue, prior = prior,
         data = data_i, sample_prior = "only",iter = 4000, family = "bernoulli")

 
  #Making the model
m <- brm(
  left_answer ~ dif_blue,
  data = data_i,
  prior = prior,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123 # Adding a seed makes results reproducible.
) 

summary(m)

#marginal plots
jpeg(file=marginal_left_path)
marginal_effects(m)
dev.off()

marginal_effects(m, method = "fit")


#trans plot
jpeg(file=trans_left_path)
print(plot(m))
dev.off()

#pp_check plot
jpeg(file=pp_left_path)
pp_check(prior_check, nsamples = 100)
dev.off()



```


```{r trying to predict but not really working out }
## predicted responses
nd <- tibble(dif_blue = (seq(from = -4, to = 4, by = 1)))

nd <- tibble(dif_blue = (seq(from = 0, to = 1, by = 1)))

pp <- predict(m,  allow_new_levels = T, sample_new_levels = "gaussian", newdata = nd, summary = FALSE)
head(pp)



pp <- predict(m)

# it will use the training data set to generate predictions
y.pred = predict(m, type="response", allow_new_levels = T, sample_new_levels = "gaussian", newdata = nd, summary = FALSE)
plot(data_i$dif_blue, y.pred, col=(round(y.pred)+1))


plot(data_i$dif_blue, y.pred)


newdata = data.frame(wt = 2.1, disp = 180)

nd <- tibble(dif_blue = factor(seq(from = 0, to = 1, by = 1)))

newdata <- data.frame(dif_blue = 1)


newdata <- data.frame(dif_blue = (seq(from = -4, to = 4, by = 1)),
                      left_answer = c(0, 1))


y.pred = predict(m, newdata = , type="response", allow_new_levels = T,  nsamples = NULL, re_formula = NULL, summary = FALSE)



```







#Individual performance

```{r logistic regression using wide format, individual left}

#LEFT 

#Getting priors
get_prior(left_answer ~ dif_blue, data = data)

#Making a number of iterations variable
n = 1

###Making a loop for individual slope
for (i in unique(left_data$unique_ID_left)){
  
  data_i <- filter(left_data, unique_ID_left == i)
  
  #path for transission plot
  trans_left_path = file.path("/Users/signeklovekjaer/Documents/CognitiveScience/4.semester/Social_and_cultural_dynamics_in_cognition/Exam/SocKultExam/plots/transition/left/", paste("trans_left_plot_", i, ".jpeg", sep = ""))
  
  #path for pp_check plot
  pp_left_path = file.path("/Users/signeklovekjaer/Documents/CognitiveScience/4.semester/Social_and_cultural_dynamics_in_cognition/Exam/SocKultExam/plots/pp_check/left/", paste("pp_left_plot_",i, ".jpeg", sep = ""))
  
  marginal_left_path = file.path("/Users/signeklovekjaer/Documents/CognitiveScience/4.semester/Social_and_cultural_dynamics_in_cognition/Exam/SocKultExam/plots/marginal/left/", paste("marginal_left_plot_",i, ".jpeg", sep = ""))
  
  #Defining priors
  prior =  c(
  prior(normal(0,2), class = "Intercept"), #How to motiavte this?
  #prior(normal(0,2), class = "sigma"), #Roughly on the same scale
  prior(normal(0,2), class = "b"), #How to motiavte this?
  prior(normal(0,1), class = "b", coef = "dif_blue"))
  
  #Prior predictive check
  prior_check <- brm( left_answer ~ dif_blue, prior = prior,
           data = data_i, sample_prior = "only",iter = 4000, family = "bernoulli")
  
  #pp_check plot
  jpeg(file=pp_left_path)
  print(pp_check(prior_check, nsamples = 100))
  dev.off()
 
  #Making the model
  m <- brm(
    left_answer ~ dif_blue,
    data = data_i,
    prior = prior,
    family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
    seed = 123 # Adding a seed makes results reproducible.
  ) 
  #marginal plot
  jpeg(file=marginal_left_path)
  print(marginal_effects(m))
  dev.off()
  
  #trans plot
  jpeg(file=trans_left_path)
  print(plot(m))
  dev.off()


  summary(m)
  
  #Saving summary in temporary dataframe
  data_i$Est_int_left <- fixef(m)[1]
  data_i$Error_int_left <- fixef(m)[3]
  data_i$Est_dif_blue_left <- fixef(m)[2]
  data_i$Error_dif_blue_left <- fixef(m)[4]
  data_i$Rhat_1_left <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[1]]
  data_i$Rhat_2_left <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[2]]
  data_i$Rhat_3_left <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[3]]
  data_i$Ess_1_left <- m[["fit"]]@.MISC[["summary"]][["ess"]][[1]]
  data_i$Ess_2_left <- m[["fit"]]@.MISC[["summary"]][["ess"]][[2]]
  data_i$Ess_3_left <- m[["fit"]]@.MISC[["summary"]][["ess"]][[3]]
  
  #Insert into permanent data frame
  if (n == 1){
    Results <- data_i
  } else {
    Results <- rbind(Results, data_i)
  }
  
n = n + 1
  
}


table(unique(Results$Image_1))
table(Results$Image_1)
length(unique(Results$Image_2))

```




```{r logistic regression using wide format, individual right}

#RIGHT

#Making a number of iterations variable
n = 1

###Making a loop for individual slope
for (i in unique(right_data$unique_ID_right)){
  data_i <- filter(right_data, unique_ID_right == i)
  
  #path for transsion plot
  #trans_right_path = file.path("~/SocKultExam/plots/transition/right/", paste("trans_right_plot_", unique_ID_right,".jpeg", sep = ""))
  
  #path for pp_check
  #pp_right_path = file.path("~/SocKultExam/plots/pp_check/right/", paste("pp_right_plot_", unique_ID_right,".jpeg", sep = ""))
  
  #Defining priors
  prior =  c(
  prior(normal(0,2), class = "Intercept"), #How to motiavte this?
  #prior(normal(0,2), class = "sigma"), #Roughly on the same scale
  prior(normal(0,2), class = "b"), #How to motiavte this?
  prior(normal(0,1), class = "b", coef = "dif_blue"))
  
  #Prior predictive check
  #prior_check <- brm( right_answer ~ dif_blue, prior = prior,
           #data = data_i, sample_prior = "only",iter = 4000, family = "bernoulli")

 
  #Making the model
  m <- brm(
    right_answer ~ dif_blue,
    data = data_i,
    prior = prior,
    family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
    seed = 123 # Adding a seed makes results reproducible.
  ) 
  
  
  #trans plot
  #jpeg(file=trans_right_path)
  #print(plot(m))
  #dev.off()

  #pp_check plot
  #jpeg(file=pp_right_path)
  #print(pp_check(prior_check, nsamples = 100))
  #dev.off()
  
  summary(m)
  
  
  #Saving summary in temporary dataframe
  data_i$Est_int_right <- fixef(m)[1]
  data_i$Error_int_right <- fixef(m)[3]
  data_i$Est_dif_blue_right <- fixef(m)[2]
  data_i$Error_dif_blue_right <- fixef(m)[4]
  data_i$Rhat_1_right <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[1]]
  data_i$Rhat_2_right <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[2]]
  data_i$Rhat_3_right <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[3]]
  data_i$Ess_1_right <- m[["fit"]]@.MISC[["summary"]][["ess"]][[1]]
  data_i$Ess_2_right <- m[["fit"]]@.MISC[["summary"]][["ess"]][[2]]
  data_i$Ess_3_right <- m[["fit"]]@.MISC[["summary"]][["ess"]][[3]]
  
  #Insert into permanent data frame
  if (n == 1){
    Results <- data_i
  } else {
    Results <- rbind(Results, data_i)
  }
  
n = n + 1
  
}


```

#Joint performance

```{r logistic regression using wide format, joint}
###JOINT
#Recoding joint answer to be 0 and 1's, 0 right, 1 left, NA = no leader
joint_data$joint_answer[joint_data$joint_answer == 0] <- NA #Replacing 0's with NA
joint_data$joint_answer[joint_data$joint_answer == -1] <- 0

#Making a number of iterations variable
n = 1

###Making a loop for individual slope
for (i in unique(joint_data$GroupNumber)){
  data_i <- filter(joint_data, GroupNumber == i)
  
  #path for transission plot
  trans_joint_path = file.path("~/SocKultExam/plots/transition/joint/", paste("trans_joint_plot_", GroupNumber, ".jpeg", sep = ""))
  
  #path for pp_check plot
  pp_joint_path = file.path("~/SocKultExam/plots/pp_check/joint/", paste("pp_joint_plot_", GroupNumber, ".jpeg", sep = ""))
  
  #Defining priors
  prior =  c(
  prior(normal(0,2), class = "Intercept"), #How to motiavte this?
  #prior(normal(0,2), class = "sigma"), #Roughly on the same scale
  prior(normal(0,2), class = "b"), #How to motiavte this?
  prior(normal(0,1), class = "b", coef = "dif_blue"))
  
  #Prior predictive check
  prior_check <- brm( joint_answer ~ dif_blue, prior = prior,
           data = data_i, sample_prior = "only",iter = 4000, family = "bernoulli")

 
  #Making the model
  m <- brm(
    joint_answer ~ dif_blue,
    data = data_i,
    prior = prior,
    family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
    seed = 123 # Adding a seed makes results reproducible.
  ) 

  #trans plot
  jpeg(file=trans_joint_path)
  print(plot(m))
  dev.off()

  #pp_check plot
  jpeg(file=pp_joint_path)
  print(pp_check(prior_check, nsamples = 100))
  dev.off()
  
  summary(m)
  
  #Saving summary in temporary dataframe
  data_i$Est_int_joint <- fixef(m)[1]
  data_i$Error_int_joint <- fixef(m)[3]
  data_i$Est_dif_blue_joint <- fixef(m)[2]
  data_i$Error_dif_blue_joint <- fixef(m)[4]
  data_i$Rhat_1_joint <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[1]]
  data_i$Rhat_2_joint <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[2]]
  data_i$Rhat_3_joint <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[3]]
  data_i$Ess_1_joint <- m[["fit"]]@.MISC[["summary"]][["ess"]][[1]]
  data_i$Ess_2_joint <- m[["fit"]]@.MISC[["summary"]][["ess"]][[2]]
  data_i$Ess_3_joint <- m[["fit"]]@.MISC[["summary"]][["ess"]][[3]]
  
  #Insert into permanent data frame
  if (n == 1){
    Results <- data_i
  } else {
    Results <- rbind(Results, data_i)
  }
  
n = n + 1
  
}

#Recoding joint answer to be 0 and 1's, 0 right, 1 left, NA = no leader
Results$joint_answer[Results$joint_answer == 0] <- NA #Replacing 0's with NA
Results$joint_answer[Results$joint_answer == -1] <- 0



#The outcome is in log odds scale, we can use tidybayes to transform them 

#parameters <- m1 %>% gather_draws(b_dif_blue) %>% median_hdi()
#  print(exp(parameters[c(".value",".lower",".upper")])) # exp() converts log-odds to odds


```



```{r combine results dataframes}
#Combine all dataframes
Results <- merge(Results_left, Results_right, by = c("GroupNumber", "Image_1"), all = TRUE)

Results <- merge(Results, Results_joint, by = c("GroupNumber", "Image_1"), all = TRUE)

write.csv(Results, file = "Results_sensitivity.csv")

```

```{r equality bias}
#create best and worst columns
Results$best <- ifelse(Results$Est_dif_blue_left > Results$Est_dif_blue_right, Results$Est_dif_blue_left, Results$Est_dif_blue_right )


Results$worst <- ifelse(Results$Est_dif_blue_left < Results$Est_dif_blue_right, Results$Est_dif_blue_left, Results$Est_dif_blue_right )

#create equality bias column
Results$eb <- Results$best/Results$worst
```


```{r collaborative benefit}
#compute collabirative benefit
Results$cb <- Results$Est_dif_blue_joint / Results$best 

```


```{r regression for difficulty}
#regression for difficulty left 

get_prior(Correct_left ~ dif_blue_abs, data = data)

 prior =  c(
  prior(normal(0,2), class = "Intercept"), #How to motiavte this?
  prior(normal(0,2), class = "sigma"), #Roughly on the same scale
  prior(normal(0,2), class = "b"), #How to motiavte this?
  prior(normal(0,1), class = "b", coef = "dif_blue_abs"))
  
  #Prior predictive check
  #prior_check <- brm( right_answer ~ dif_blue, prior = prior,
           #data = data_i, sample_prior = "only",iter = 4000, family = "bernoulli")

#new column with abs for dif_blue
data$dif_blue_abs <- abs(data$dif_blue)

#LOGISTIC!!!!!! change it 

#LEFT 
  #Making the model
dif_reg_left <- brm(
    Correct_left ~ dif_blue_abs + (1|unique_ID_left),
    data = data,
    prior = prior,
    family = "gaussian", #As we had a binary outcome, we set this to "bernoulli"
    seed = 123 # Adding a seed makes results reproducible.
    ) 

summary(dif_reg_left)

marginal_effects(dif_reg_left)

#RIGHT
dif_reg_right <- brm(
    Correct_right ~ dif_blue_abs + (1|unique_ID_right),
    data = data,
    prior = prior,
    family = "gaussian", #As we had a binary outcome, we set this to "bernoulli"
    seed = 123 # Adding a seed makes results reproducible.
    ) 

summary(dif_reg_right)

marginal_effects(dif_reg_right)


#JOINT
dif_reg_joint <- brm(
    Correct_joint ~ dif_blue_abs + (1|GroupNumber),
    data = data,
    prior = prior,
    family = "gaussian", #As we had a binary outcome, we set this to "bernoulli"
    seed = 123 # Adding a seed makes results reproducible.
    ) 

summary(dif_reg_joint)

marginal_effects(dif_reg_joint)

```




#Making long format
This is in order to calculate the equality bias

```{r making long format, include = FALSE}
#take just the columns we need
#L_data <- subset(Results, select = c(GroupNumber, SubjectID_right, SubjectID_left, Gender_left, Gender_right, Familiarity, dif_blue, left_answer, right_answer, joint_answer ))


#change to long format 

L_data <- melt(Results, 
                     variable.name = "Position",
                     value.name = "Subject",
                     id.vars = c("GroupNumber", "Gender_left", "Gender_right", "Familiarity", "dif_blue", "left_answer", "right_answer", "joint_answer"))

```


- logistic regression individuals and joint - plot 
  - posterior predictive for one participant 
- calculate equality bias (best/worst)
- calculate collaborative bias (joint/best)
- Regression for difficulty 
- write csv with results

```{r}
#take just the columns we need
test_data <- subset(data, select = c(GroupNumber, unique_ID_left, unique_ID_right, dif_blue, left_answer, right_answer, joint_answer, Correct_left, Correct_right, Correct_joint, dif_blue_abs))


#change to long format 

L_data <- melt(test_data, 
                     variable.name = "Position",
                     value.name = "Subject",
                     id.vars = c("GroupNumber", "dif_blue", "left_answer", "right_answer", "joint_answer", "Correct_left", "Correct_right", "Correct_joint", "dif_blue_abs"))
```


```{r}
left <- subset(data, select = c(GroupNumber, unique_ID_left, dif_blue, left_answer, joint_answer, Correct_left, Correct_joint, dif_blue_abs))

names(left) <- c("GroupNumber", "unique", "dif_blue", "answer", "joint_answer", "Correct", "Correct_joint", "dif_blue_abs")

right <- subset(data, select = c(GroupNumber, unique_ID_right, dif_blue, right_answer, joint_answer, Correct_left, Correct_joint, dif_blue_abs))

names(right) <- c("GroupNumber", "unique", "dif_blue", "answer", "joint_answer", "Correct", "Correct_joint", "dif_blue_abs")
```


```{r joint models }

ldata <- rbind(left, right)

get_prior(answer ~ dif_blue + GroupNumber, data = ldata)


#Defining priors
prior_joint =  c(
  prior(normal(0,2), class = "Intercept"), 
  prior(normal(0,2), class = "sigma"), #Why does this not work? 
  prior(normal(0,2), class = "b"), 
  prior(normal(0,1), class = "b", coef = "dif_blue"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber11"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber12"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber13"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber14"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber15"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber16"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber17"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber18"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber19"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber20"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber21"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber22"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber23"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber24"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber25"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber26"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber27"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber28"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber29"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber30"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber31"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber32"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber33"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber34"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber35"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber36"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber37"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber38"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber39"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber40"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber10"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber9"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber8"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber7"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber6"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber5"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber4"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber3"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber2"), 
  prior(normal(0,1), class = "b", coef = "GroupNumber1")
  
 )

#Joint model with answer
m_joint_answer <- brm(
  
  joint_answer ~ dif_blue + GroupNumber,
  data = ldata,
  prior = prior_joint,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123 # Adding a seed makes results reproducible.
  
  ) 
  
summary(m_joint_answer)


#Joint model with correct
m_joint_correct <- brm(
  
  Correct_joint ~ dif_blue + GroupNumber,
  data = ldata,
  prior = prior_joint,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123 # Adding a seed makes results reproducible.
  
  ) 
  
summary(m_joint_correct)
```

