g---
title: "after_riccardo_analysis"
author: "Signe Kløve Kjær"
date: "13/5/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setting working directory}
#set working directory 
setwd("/Users/signeklovekjaer/Documents/CognitiveScience/4.semester/Social_and_cultural_dynamics_in_cognition/Exam/SocKultExam/") #Signe
#setwd("~/SocKultExam") #Thea

```

```{r loading libraries}
#load libraries
library(pacman)
p_load(lme4, lmerTest, brms, tidyverse, stringi, tm)

```

##PREPARE POOLING DATA

```{r load data}
#read csv files with estimates
pool_estimates <- read.csv("pooling_individual_wide.csv")
```


```{r clean pooling data}

#Change names for sensitivity slopes
names(pool_estimates)[names(pool_estimates) == 'Slope_ranef_fixef_estimate_answer_left'] <- 'Est_dif_blue_left_answer'

names(pool_estimates)[names(pool_estimates) == 'Slope_ranef_fixef_estimate_answer_right'] <- 'Est_dif_blue_right_answer'

names(pool_estimates)[names(pool_estimates) == 'Slope_ranef_fixef_estimate_correct_left'] <- 'Est_dif_blue_left_correct'

names(pool_estimates)[names(pool_estimates) == 'Slope_ranef_fixef_estimate_correct_right'] <- 'Est_dif_blue_right_correct'


#Create chosen-leader-column 
pool_estimates$chosen_leader <- ifelse(pool_estimates$right_answer == pool_estimates$left_answer, "Agree", 0) #create a column that sorts out all the agreed trials

#Create variable, which determines the chosen leader
pool_estimates$chosen_leader[pool_estimates$chosen_leader == 0 & pool_estimates$Joint_right == 0] <- "Left_lead"
pool_estimates$chosen_leader[pool_estimates$chosen_leader == 0 & pool_estimates$Joint_left == 0] <- "Right_lead"

#create column that specifies the gender of the leader
pool_estimates$Leader_gender <- 0
pool_estimates$Leader_gender <- ifelse(pool_estimates$chosen_leader == "Left_lead", as.character(pool_estimates$Gender_left), as.character(pool_estimates$Gender_right))
pool_estimates$Leader_gender[pool_estimates$chosen_leader == "Agree"] <- NA

#create column that specifies the gender of the follower
pool_estimates$Follower_gender <- 0
pool_estimates$Follower_gender <- ifelse(pool_estimates$chosen_leader == "Left_lead", as.character(pool_estimates$Gender_right), as.character(pool_estimates$Gender_left))
pool_estimates$Follower_gender[pool_estimates$chosen_leader == "Agree"] <- NA


#create stubborn leader
pool_estimates$Stubborn_leader <- 0 #Creating column of 0's

pool_estimates$Stubborn_leader[pool_estimates$chosen_leader == "Right_lead" & pool_estimates$joint_answer == pool_estimates$right_answer] <- "stick" #Inserting cases were leader stick for right leader
pool_estimates$Stubborn_leader[pool_estimates$chosen_leader == "Right_lead" & pool_estimates$joint_answer != pool_estimates$right_answer] <- "surrender" #Inserting cases were leader surrender for right leader

pool_estimates$Stubborn_leader[pool_estimates$chosen_leader == "Left_lead" & pool_estimates$joint_answer == pool_estimates$left_answer] <- "stick" #Inserting cases were leader stick for left leader
pool_estimates$Stubborn_leader[pool_estimates$chosen_leader == "Left_lead" & pool_estimates$joint_answer != pool_estimates$left_answer] <- "surrender" #Inserting cases were leader surreder for left leader

pool_estimates$Stubborn_leader[pool_estimates$chosen_leader == "Agree"] <- NA #Removing cases were they agree


#code leader and follower gender as dummies, 0 = male, 1 = female
pool_estimates$Leader_gender[pool_estimates$Leader_gender == "Male"] <- 0

pool_estimates$Leader_gender[pool_estimates$Leader_gender == "Female"] <- 1

pool_estimates$Follower_gender[pool_estimates$Follower_gender == "Male"] <- 0

pool_estimates$Follower_gender[pool_estimates$Follower_gender == "Female"] <- 1


#Rename stubborn-leader-column
names(pool_estimates)[names(pool_estimates) == 'Stubborn_leader'] <- 'Surrender'

pool_estimates$Surrender <- as.character(pool_estimates$Surrender)

#dummy code surrender columns, surrender = 1, stick = 0
pool_estimates$Surrender[pool_estimates$Surrender == "surrender"] <- 1

pool_estimates$Surrender[pool_estimates$Surrender == "stick"] <- 0

pool_estimates$Surrender[pool_estimates$chosen_leader == "Agree"] <- NA

#rename confidence
names(pool_estimates)[names(pool_estimates) == 'Response_left'] <- 'confidence_left'
names(pool_estimates)[names(pool_estimates) == 'Response_right'] <- 'confidence_right'

pool_data <- pool_estimates
```


```{r calculate skill difference}

#Calculating skill difference

#for answer
pool_estimates$skill_dif_answer <- 0 #Creating column of 0
pool_estimates$skill_dif_answer <- ifelse(pool_estimates$chosen_leader == "Left_lead", pool_estimates$Est_dif_blue_left_answer/pool_estimates$Est_dif_blue_right_answer, pool_estimates$Est_dif_blue_right_answer/pool_estimates$Est_dif_blue_left_answer) #calculating skill difference as a ratio between leader and follower sensitivity

pool_estimates$skill_dif_answer[pool_estimates$chosen_leader == "Agree"] <- NA #Insert NAs in all agree trials

#for correct
pool_estimates$skill_dif_correct <- 0 #Creating column of 0
pool_estimates$skill_dif_correct <- ifelse(pool_estimates$chosen_leader == "Left_lead", pool_estimates$Est_dif_blue_left_correct/pool_estimates$Est_dif_blue_right_correct, pool_estimates$Est_dif_blue_right_correct/pool_estimates$Est_dif_blue_left_correct) #calculating skill difference as a ratio between leader and follower sensitivity

pool_estimates$skill_dif_correct[pool_estimates$chosen_leader == "Agree"] <- NA #Insert NAs in all agree trials

```


```{r make long format}
#Subset to left data
pool_left <- subset(pool_data, select = c(GroupNumber, unique_ID_left, dif_blue, dif_blue_abs, chosen_leader, Leader_gender, Follower_gender, skill_dif_correct, skill_dif_answer, confidence_left, Surrender)) #take all data for left participant

pool_left$skill_dif_answer[pool_left$chosen_leader != 'Left_lead'] <- NA #insert NAs for chosen leader if not left
pool_left$skill_dif_correct[pool_left$chosen_leader != 'Left_lead'] <- NA #insert NAs for chosen leader if not left

pool_left$Surrender[pool_left$chosen_leader != 'Left_lead'] <- NA #insert NAs for chosen leader if not left
pool_left$Leader_gender[pool_left$chosen_leader != 'Left_lead'] <- NA #insert NAs for chosen leader if not left
pool_left$Follower_gender[pool_left$chosen_leader != 'Left_lead'] <- NA #insert NAs for chosen leader if not left

#Subset right data
pool_right <- subset(pool_data, select = c(GroupNumber, unique_ID_right, dif_blue, dif_blue_abs, chosen_leader, Leader_gender, Follower_gender, skill_dif_correct, skill_dif_answer, confidence_right, Surrender)) #Subsetting right data

pool_right$skill_dif_answer[pool_right$chosen_leader != 'Right_lead'] <- NA #insert NAs for chosen leader if not right
pool_right$skill_dif_correct[pool_right$chosen_leader != 'Right_lead'] <- NA #insert NAs for chosen leader if not right

pool_right$Surrender[pool_right$chosen_leader != 'Right_lead'] <- NA #insert NAs for chosen leader if not right

pool_right$Leader_gender[pool_right$chosen_leader != 'Right_lead'] <- NA #insert NAs for chosen leader if not right

pool_right$Follower_gender[pool_right$chosen_leader != 'Right_lead'] <- NA #insert NAs for chosen leader if not right

#Renaming the columns to match
names(pool_left) <- c("GroupNumber", "unique_ID", "dif_blue", "dif_blue_abs", "chosen_leader", "Leader_gender", "Follower_gender", "skill_dif_correct", "skill_dif_answer", "confidence", "Surrender")

names(pool_right) <- c("GroupNumber", "unique_ID", "dif_blue", "dif_blue_abs", "chosen_leader", "Leader_gender", "Follower_gender", "skill_dif_correct", "skill_dif_answer", "confidence", "Surrender")

#Rbinding left and right data
pool_long <- rbind(pool_left, pool_right)

#Removing all agree trials
pool_disagree <- na.omit(pool_long)

#Renaming unique_ID column
names(pool_disagree)[names(pool_disagree) == 'unique_ID'] <- 'Subject'

#Removing outliers for the answer model
pool_disagree_outlier_rem <- subset(pool_disagree, Subject != "14_signekirk")

pool_disagree_outlier_rem$Subject <- as.character(pool_disagree_outlier_rem$Subject)
pool_disagree_outlier_rem$Subject <- tolower(pool_disagree_outlier_rem$Subject)

pool_disagree_outlier_rem$Subject <- str_extract(pool_disagree_outlier_rem$Subject,"[a-z]+")

#make confidence absolute 
#pool_long$Confidence <- abs(pool_long$Confidence)

#remove the groupnumber from subject name to account for within participant variation
pool_disagree$Subject <- as.character(pool_disagree$Subject)
pool_disagree$Subject <- tolower(pool_disagree$Subject)

pool_disagree$Subject <- str_extract(pool_disagree$Subject,"[a-z]+")


```


#MODELS
```{r run the answer model with skill difference}
#Get priors
get_prior(Surrender ~ skill_dif_answer * Leader_gender * Follower_gender + (1 + skill_dif_answer:Follower_gender | Subject ), data = pool_disagree_outlier_rem, family = "bernoulli")

#Defining priors
prior_answer <- c(
  prior(normal(0,1),class="Intercept"),
  prior(normal(0,.2),class="b"),
  prior(normal(0,.1),class="sd")
)

#prior predictive check
prior_check_answer <- brm(Surrender ~ skill_dif_answer * Leader_gender * Follower_gender + (1 + skill_dif_answer:Follower_gender | Subject ), prior = prior_answer, data = pool_disagree_outlier_rem, sample_prior = "only",iter = 4000, family = "bernoulli", chains = 2, cores = 2)

pp_check(prior_check_answer, nsamples = 100)

# Model w skill difference
m_answer <- brm(
  Surrender ~ skill_dif_answer * Leader_gender * Follower_gender + (1 + skill_dif_answer:Follower_gender | Subject ),
  data = pool_disagree_outlier_rem,
  prior = prior_answer,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  cores=2,
  chains=2,
  control = list(adapt_delta = 0.9) #only for answer model, due to Eff.Sample
) 

summary(m_answer)
```


<<<<<<< HEAD:after_riccardo_analyss.Rmd

=======
>>>>>>> a864b8b623ed8af5a575d38016f13d5128046c44:Earlier editions of scripts, not actual/after_riccardo_analyss.Rmd
```{r model without skill difference}
#Defining priors
prior_0 <- c(
  prior(normal(0,.2),class="b"),
  prior(normal(0,.1),class="sd")
)

#prior predictive check
prior_check_0 <- brm(Surrender ~ 0 + Leader_gender : Follower_gender + (0 + Follower_gender | Subject ), prior = prior_0, data = pool_disagree, sample_prior = "only",iter = 4000, family = "bernoulli", chains = 2, cores = 2)

pp_check(prior_check_0, nsamples = 100)

#model without skill difference
m_0 <- brm(
  Surrender ~ 0 + Leader_gender : Follower_gender + (0 + Follower_gender | Subject ),
  data = pool_disagree,
  prior = prior_0,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=2,
  cores=2
) 

marginal_effects(m_0)

```



#MODEL COMPARISON

```{r answer and correct}
waic(m_answer, m_correct)

```

```{r all}
waic(m_correct, m_answer, m_0)

compare(m_correct, m_answer)

waic(m_answer, m_0)


marginal_effects(m_answer)

marginal_effects(m_0)

marginal_effects(m_correct)

4+4

```



#### #### #### #### #### #### HYPOTHESIS TESTING #### #### #### #### #### #### 



# H1: there is a leader effect: male leaders tend to surrender less than female leaders
```{r H1: there is a leader effect: male leaders tend to surrender less than female leaders}
#H1: In general male leader tend to surrender more than female leaders

hypothesis(m_0, "(Leader_gender0:Follower_gender0 + Leader_gender0:Follower_gender1)/2 < (Leader_gender1:Follower_gender0 + Leader_gender1:Follower_gender1)/2")



```

# H1: plotting
```{r}


```


#H2: there is a follower effect: leaders tend to surrender more to men than to women
```{r H2: there is a follower effect: leaders tend to surrender more to men than to women }

# H2: There is a follower effect: leaders tend to surrender more to men than to women
hypothesis(m_0, "(Leader_gender0:Follower_gender0 + Leader_gender1:Follower_gender0)/2 > (Leader_gender0:Follower_gender1 + Leader_gender1:Follower_gender1)/2")




```

# H2: plotting
```{r}

```


```{r H3: there is an interaction, males are more discriminative as to their followers gender than females are }
# H3: There is an interaction: males are more discriminative as to their followers gender than females are

hypothesis(m_0, "(Leader_gender0:Follower_gender0 - Leader_gender0:Follower_gender1) > (Leader_gender1:Follower_gender0 - Leader_gender1:Follower_gender1)")
```


# H3: plotting
```{r}

```








